### 2009-11-27 doc/tech_doc/client/client_technical.tex
Moved API documentation from client_technical.tex to appropriate header files as doxygen documentation

\chapter{Implementation}
\label{sec:Implementation}

In this section an overview of all important classes in the new
{\libarcclient} is given. The overview is subdivided in two parts where
first all the generic classes are presented,
Section~\ref{sec:genclass}, before the grid flavour specializations
are presented in Section~\ref{sec:plugins}. Classes are described both
in words and by code.

\section{Generic Classes}
\label{sec:genclass}

\subsection{{\ACC}}

The Arc Client Component ({\ACC}) class is a base class needed for the
{\Loader} in order to create loadable classes. It stores information
about which flavour it supports and security related information
needed by all ACC specializations.

\begin{shaded}
\begin{verbatim}
class ACC {
protected:
  ACC(Config *cfg, const std::string& flavour);
public:
  virtual ~ACC();
  const std::string& Flavour();
protected:
  std::string flavour;
  std::string proxyPath;
  std::string certificatePath;
  std::string keyPath;
  std::string caCertificatesDir;
};
\end{verbatim}
\end{shaded}

\subsection{{\TargetGenerator}}

The {\TargetGenerator} class is the main class for resource discovery
and information retrieval. It loads {\TargetRetriever} plugins in
accordance with the input {\URL}s using the ARC {\Loader}~\cite{hed}
(e.g.\ if an {\URL} pointing to an ARC1 resource is given the
TargetRetrieverARC1 is loaded).

To perform a resource discovery, first construct a {\TargetGenerator}
object using the {\TargetGenerator} constructor,

\begin{shaded}
\begin{verbatim}
TargetGenerator(const UserConfig& usercfg,
                const std::list<std::string>& clusters,
                const std::list<std::string>& indexurls);
\end{verbatim}
\end{shaded}

where \texttt{clusters} and \texttt{indexurls} are lists of strings
where each string is either the name of a grid flavour followed by a
colon and the URL of an information contact endpoint for a computing
service or index server, respectively, of that grid flavour or an
alias defined in the {\UserConfig} object passed as the first
argument, e.g.:

\begin{shaded}
\begin{small}
\begin{verbatim}
ARC0:ldap://grid.tsl.uu.se:2135/Mds-Vo-name=Sweden,o=grid
ARC0:ldap://grid.tsl.uu.se:2135/nordugrid-cluster-name=grid.tsl.uu.se,Mds-Vo-name=local,o=grid
\end{verbatim}
\end{small}
\end{shaded}

where the former is the URL to an index server while the latter is an
URL to a computing service. If a string in \texttt{clusters} or
\texttt{indexurls} is prefixed by a minus sign, the corresponding
computing service or index server is rejected and excluded during
resource discovery.

To prepare a list of {\ExecutionTarget}s use the {\TargetGenerator}
object and invoke its method

\begin{shaded}
\begin{verbatim}
GetTargets(int targetType, int detailLevel);
\end{verbatim}
\end{shaded}

The {\TargetGenerator} will pass this request to the loaded
{\TargetRetriever}s running them as individual threads for improved
performance. The {\TargetGenerator} keeps records of index servers and
computing services found by the {\TargetRetriever}s in order to avoid
multiple identical queries. Accepted {\ExecutionTarget}s are stored in
the FoundTargets array kept by the {\TargetGenerator}. See also
Section~\ref{sec:TargetDiscovery} for a schematic drawing of the
resource discovery process.

Information about the found {\ExecutionTarget}s can be printed by

\begin{shaded}
\begin{verbatim}
PrintTargetInfo(bool longlist) const;
\end{verbatim}
\end{shaded}

\subsection{{\TargetRetriever}}

The {\TargetRetriever} is the base class for grid middleware specialized 
{\TargetRetriever}s and inherits from the {\ACC} base class in
order to be loadable by the ARC \texttt{Loader}. It is designed to
work in conjunction with the {\TargetGenerator} and contains the pure
virtual method

\begin{shaded}
\begin{verbatim}
virtual void GetTargets(TargetGenerator& mom, int targetType,
                        int detailLevel) = 0;
\end{verbatim}
\end{shaded}

which is to be implemented by the specialized class. While it is not
mandatory it is recommended that the specialized class divides this
method into two components: QueryIndex and InterrogateTarget. The
former handles index server queries, and the latter the computing
service queries and {\ExecutionTarget} preparation.

If an index server query yields a URL to a different index server
than the one queried, then the {\TargetRetriever} should call itself
recursively creating a new {\TargetRetriever} for the discovered index
server.

\subsection{{\ExecutionTarget}}

The {\ExecutionTarget} is the class representation of a computing
resource (queue) capable of executing a grid job. It serves as input
to the {\Broker} which is able to filter and rank different 
{\ExecutionTarget}s from different grid flavours without a
priori knowing their difference. The {\ExecutionTarget} class mimics
the Glue2 information model (with a flattened structure), and thus a
mapping between attributes from other information systems into the
Glue2 format is needed. Appendix \ref{app:ExTarget} shows the current
mapping for the production ARC, ARC1 and gLite middlewares.

All attributes of the {\ExecutionTarget} can be printed by the method

\begin{shaded}
\begin{verbatim}
void Print(bool longlist) const;
\end{verbatim}
\end{shaded}

All information needed to submit a job is stored in the {\ExecutionTarget}, 
and the {\ExecutionTarget}'s method

\begin{shaded}
\begin{verbatim}
Submitter *GetSubmitter(const UserConfig& ucfg) const;
\end{verbatim}
\end{shaded}

returns a {\Submitter} which is used to submit jobs. The {\UserConfig} object 
is used to configure the security related information needed by the {\Submitter}.

\subsection{{\Broker}}

@@

\subsection{{\JobDescription}}

When addressing interoperability it is of paramount importance to
transparently address grid job descriptions written in different job
description languages by translating them automatically. In the
{\libarcclient} library this functionality is implemented in the
{\JobDescription} class which parses job descriptions given in the 
XRSL~\cite{xrsl}, JDL~\cite{jdl} or JSDL~\cite{jsdl} formats into an 
internal representation based upon the upcoming PGI-JSDL proposal.

\begin{shaded}
\begin{verbatim}
bool setSource(const std::string source);
bool setSource(const XMLNode& source);
\end{verbatim}
\end{shaded}

The setSource method takes a source job description string as input and identifies it's format 
(language) through pattern matching (the \texttt{JobDescriptionOrderer} class).
Once the format is known, the source elements are mapped from the original format (XRSL, JDL or JSDL) 
into an internal representation (the \texttt{JobInnerRepresentation} class). Mapping details 
are given in Section~\ref{app:jobinnerrepresentation}.

The {\JobDescription} class has three back-end classes, sometimes
referred to as back-end or translator modules, corresponding to the
three supported job description languages. The {\JobDescription} class
chooses the appropriate back-end module according to the pattern matching
performed by the \texttt{JobDescriptionOrderer}, and uses the back-end
module for parsing and translation (if needed) of the job descriptions.

Once the job description language required by the {\ExecutionTarget} chosen 
for job submission is known, the parsed and (if needed) translated job description 
can be retrieved through the {\texttt GetProduct} function as shown below:

\begin{shaded}
\begin{verbatim}
bool getProduct(std::string& product, std::string format = "POSIXJSDL") const;
\end{verbatim}
\end{shaded}

If the inner representation is empty or the source job description is not
valid, then the {\texttt GetProduct} output is empty too and the method 
returns with false.  In order to obtain the automatic job description 
modifications similar to those of the production ARC client, the 
{\texttt GetProduct} output is always generated from the internal 
representation using the \texttt{JobDescriptionOrderer} class to carry 
out the translation. The original source string can be regained by
calling the \texttt{getSourceString} method:

\begin{shaded}
\begin{verbatim}
bool getSourceString(std::string source) const;
\end{verbatim}
\end{shaded}

The translation of a job description basically means a syntactical transformation 
of the job description from one language to another. Thus the {\JobDescription}
class can do nothing in those cases where there is not enough data available 
to assemble a given attribute or when information can be lost because the received 
attribute has no equivalent in the output language. In these cases the {\texttt GetProduct} 
method returns with a false value and an empty product string. For limitations in the translation
see Section~\ref{app:jobinnerrepresentation}.

For the JSDL output generation the {\JobDescription} class uses
the core JSDL's capabilities amended with the JSDL-POSIX and JSDL-ARC
extensions. The loss of information is minimal in case of generating
such an output.

For the JDL generation the latest version of JDL specification was
used (v0.9) \cite{jdl}. Deprecated and backward compatibility
attributes are not implemented.

In case of job resubmission the internal representation will contain a list of 
the jobid's of the previous jobs. This element will only be parsed to the 
actually job description in case JSDL-POSIX output is requested. A new URL 
can be added to the list of old jobid's by using the method:

\begin{shaded}
\begin{verbatim}
bool addOldJobID(const URL& oldjobid);
\end{verbatim}
\end{shaded}

\subsection{{\Submitter}}

{\Submitter} is the base class for grid middleware specialized {\Submitter}s (plugins).
It submits job(s) to the service it represents and uploads (needed by the job) local 
input files.

\begin{shaded}
\begin{verbatim}
virtual bool Submit(const JobDescription& jobdesc, XMLNode& info) const = 0;
\end{verbatim}
\end{shaded}

The \texttt{Submit} method fills the {\XMLNode} \texttt{info} with all
needed information about the job for later job management. The
{\Submitter} is returned by the {\ExecutionTarget} selected for job
execution and thus the {\ExecutionTarget} populates (through its
{\XMLNode} config element) the {\Submitter} with information about
submission endpoint ({\URL}) and job description languages understood
by the target.

\begin{shaded}
\begin{verbatim}
virtual bool Migrate(const URL& url,
                     const JobDescription& jobdesc,
                     bool forcemigration,
                     XMLNode& info) const = 0;
\end{verbatim}
\end{shaded}

The \texttt{Migrate} method behaves in much the same way as the \texttt{Submit}
method, but instead of sending a new job request to the cluster it sends a 
migration request of a given job, currently this request is only supported 
for ARC1 clusters. The \texttt{URL} and \texttt{jobdesc} specifies the job-id 
and {\JobDescription} of the job which should be migrated.

Note that whereas the \texttt{Migrate} method make provisions for automatically 
getting files from the migration source cluster, this does not apply to the job 
description which instead should be passed to \texttt{Migrate} explicitly in the 
form of a {\JobDescription} object.

The migration request will create a new job where the local input files are 
transferred from old cluster. Once the input files have been transferred the 
new cluster will send a request to kill the old job. If the kill request is 
unsuccessful the new job will be terminated unless the \texttt{forcemigration} 
boolean is \texttt{true}.

The \texttt{Migrate} method will also fill the \texttt{info} {\XMLNode} with 
information about the job the same way as the \texttt{Submit} method. However 
for the \texttt{Migrate} method this \texttt{XMLNode} also contain the job-id 
of the migrated job.

\subsection{{\JobSupervisor}}

The {\JobSupervisor} is responsible for loading the appropriate
{\JobController}s for managing jobs running on a certain grid
flavour. Job manipulation can be performed either on individual jobs
or on groups of jobs (e.g.\ all jobs running on certain cluster or all
jobs with job state ``FINISHED''), and in order to translate the
information given by the user into a set of loadable {\JobController}s
the {\JobSupervisor} makes extensive use of the local joblist file
which house information about all active jobs. Thus the {\JobSupervisor}
constructor becomes

\begin{shaded}
\begin{verbatim}
JobSupervisor(const UserConfig& usercfg,
              const std::list<std::string>& jobs,
              const std::list<std::string>& clusters,
              const std::string& joblist);
\end{verbatim}
\end{shaded}

where \texttt{jobs} is a list of job identifiers and job names,
\texttt{clusters} is a list of selected and rejected computing
services in the same format as described above for the
{\TargetGenerator}, \texttt{joblist} is a string containing the name
of the joblist file.

Although loaded by the {\JobSupervisor} the {\JobController}
objects actually reside within the ARC {\Loader} which is a member of
the {\JobSupervisor} class. In order to get handles on the
{\JobController}s, the inline method

\begin{shaded}
\begin{verbatim}
const std::list<JobController*>& GetJobControllers();
\end{verbatim}
\end{shaded}

returns a list of pointers to the loaded {\JobController}s.

\subsection{{\JobController}}

The {\JobController} is a base class for grid specific
specializations, but also the implementer of all public functionality
offered by the {\JobController}s. In other words all virtual functions
of the {\JobController} are private. The initialization of a
(specialized) {\JobController} object takes two steps. First the
{\JobController} specialization for the required grid flavour must be
loaded by the ARC {\Loader}, which sees to that the {\JobController}
receives information about its flavour (grid) and the local joblist
file containing information about all active jobs (flavour
independent). The next step is the filling of the {\JobController}'s job
pool \texttt{JobStore} which is the pool of jobs that the
{\JobController} can manage.

\begin{shaded}
\begin{verbatim}
void FillJobStore(const std::list<URL>& jobids,
                  const std::list<URL>& clusterselect,
                  const std::list<URL>& cluterreject);
\end{verbatim}
\end{shaded}

Here \texttt{jobids}, \texttt{clusterselect} and
\texttt{clusterreject} have been resolved for job names and aliases by
the {\JobSupervisor}, and no further resolution is needed. The
following rules are observed when filling the \texttt{JobStore}:

\begin{enumerate}
\item{If the \texttt{jobids} list has entries, fill \texttt{JobStore}
  with the jobs requested by the user.}
\item{If the \texttt{clusterselect} list has entries, fill
  \texttt{JobStore} with the jobs running on the selected clusters.}
\item{If clusters are rejected and \texttt{JobStore} has entries,
  remove from \texttt{JobStore} all jobs running on rejected
  clusters.}
\item{If \texttt{jobids} and \texttt{clusterselect} are both empty
  lists, fill \texttt{JobStore} with all jobs except those running on
  rejected clusters if there are any.}
\end{enumerate}

The steps above complete the initialization of the {\JobController}
which is now ready for handling jobs. The public functions of the
{\JobController} offer to get (download), clean, cancel, etc. one or
more jobs and use the virutal methods implemented by the grid middleware 
specialized {\JobController}s for issuing the command. Here exemplified 
by the \texttt{Stat} command:

\begin{shaded}
\begin{small}
\begin{verbatim}
bool JobController::Stat(const std::list<std::string>& status,
                         const bool longlist,
                         const int timeout) {

  GetJobInformation();

  for (std::list<Job>::iterator it = jobstore.begin();
       it != jobstore.end(); it++) {
    if (it->State.empty()) {
      logger.msg(WARNING, "Job state information not found: %s",
                 it->JobID.str());
      Time now;
      if (now - it->LocalSubmissionTime < 90)
        logger.msg(WARNING, "This job was very recently "
                   "submitted and might not yet"
                   "have reached the information-system");
      continue;
    }
    it->Print(longlist);
  }
  return true;
}
\end{verbatim}
\end{small}
\end{shaded}

The \texttt{Stat} command prints the job information to screen and in
order to do so the {\JobController} has to query local information
server for the latest status. Due to different protocols used for
different grid flavours (e.g.\ ldap for production ARC), the
\texttt{GetJobInformation} has to be grid flavour specific and is only
declared as a private virtual method within the {\JobController} base
class. For details about the flavour specific implementations see
Section~\ref{sec:plugins}.

The other public methods of the {\JobController} class are:
The \texttt{Get} which is used to download jobs
\begin{shaded}
\begin{verbatim}
bool Get(const std::list<std::string>& status, const std::string& downloaddir,
         const bool keep, const int timeout);
\end{verbatim}
\end{shaded}
\begin{shaded}
\begin{verbatim}
bool Kill(const std::list<std::string>& status, const bool keep, const int timeout);
\end{verbatim}
\end{shaded}
\begin{shaded}
\begin{verbatim}
bool Clean(const std::list<std::string>& status, const bool force, const int timeout);
\end{verbatim}
\end{shaded}
\begin{shaded}
\begin{verbatim}
bool Cat(const std::list<std::string>& status, const std::string& whichfile, 
         const int timeout);
\end{verbatim}
\end{shaded}
\begin{shaded}
\begin{verbatim}
bool RemoveJobs(const std::list<URL>& jobids);
\end{verbatim}
\end{shaded}
\begin{shaded}
\begin{verbatim}
std::list<std::string> GetDownloadFiles(const URL& dir);
\end{verbatim}
\end{shaded}
\begin{shaded}
\begin{verbatim}
bool CopyFile(const URL& src, const URL& dst);
\end{verbatim}
\end{shaded}
The \texttt{GetJobDescriptions} method 
\begin{shaded}
\begin{verbatim}
std::list<Job> GetJobDescriptions(const std::list<std::string>& status, 
                                  const bool getlocal, const int timeout);
\end{verbatim}
\end{shaded}
which is used to get the job descriptions of {\Job}s in the \texttt{JobStore} 
with the specified status'. In case \texttt{getlocal} is true the job description 
will first be searched for the users local XML file. If a local copy of 
the job description is found the checksum of the local input files will be 
computed and compared with the ones listed in the users local XML file. If 
all checksums match the job description is returned.

In case \texttt{getlocal} is false or the retrieval of the local job description 
fails an attempt will be made to retrieved the job description from the cluster. This has 
currently only been implemented for ARC(both generations) clusters. Note 
that the job descriptions retrieved from a cluster will most likely have 
been changed since the submission -- either by the cluster\footnote{For both 
generations of ARC it is possible to recover the initial job description send 
to the cluster. However modifications can still have been made to the 
job description before sending it to the cluster.} or by the submission 
client. Therefore, the only way of retrieving the original job description is 
through the users local XML file.

The \texttt{GetJobDescriptions} returns a list of the  {\Job}s where job description 
have been found. The found job descriptions are kept in the 
{\Job}.\texttt{JobDescription} attribute.

The \texttt{Migrate} method
\begin{shaded}
\begin{verbatim}
bool Migrate(TargetGenerator& targetGen,
             Broker* broker,
             const bool forcemigration,
             const int timeout);
\end{verbatim}
\end{shaded}
will try to migrate the jobs contained in the object ({\JobController}). The jobs
will be migrated to the targets specified in {\TargetGenerator} \texttt{targetGen}
by using the broker specified by {\Broker} \texttt{broker}. The boolean
\texttt{forcemigration} specifies whether a migrated job should persist if the
new cluster ({\ExecutionTarget}) chosen by the {\TargetGenerator} does not
succeed sending a kill/terminate request for the job. The integer
\texttt{timeout} argument has not yet been implemented.

\subsection{{\Job}}

The {\Job} is a generic job class for storing all job related
information. Attributes are derived from the Glue2 information model
and thus a mapping is needed for non Glue2 compliant grid middlewares.

All attributes of the {\Job} can be printed by the method (longlist = true 
will give more details (long listing))

\begin{shaded}
\begin{verbatim}
void Print(bool longlist) const;
\end{verbatim}
\end{shaded}

\subsection{{\UserConfig}}

The {\UserConfig} class handles the client setup i.e. proxy,
certificate and key location, user and system configuration and local
joblist location. Upon initialization (constructor) the {\UserConfig}
locates and reads the user files

\begin{shaded}
\begin{verbatim}
$HOME/.arc/client.xml
$HOME/.arc/jobs.xml
\end{verbatim}
\end{shaded}

and if either of them is non-existing a default (empty) one is created.

The {\UserConfig} has three main public methods

\begin{shaded}
\begin{verbatim}
const std::string& JobListFile() const;
const & ConfTree() const;
bool ApplySecurity(XMLNode& ccfg) const;
\end{verbatim}
\end{shaded}

where \texttt{JobListFile()} returns the string pointing to the
jobs.xml file while \texttt{ConfTree()} returns a configuration
{\XMLNode} object which is the merge between the user and system
configurations. In order to do this the method has to locate the
system configuration and resolve possible conflicts with the user
configuration. This proceeds through the following chain of actions:

\begin{enumerate}
\item{Try reading system configuration from \texttt{<ARC Install
    Location>/etc/arcclient.xml}}
\item{If the previous step failed try reading system configuration
  from \texttt{/etc/arcclient.xml}}
\item{Merge system and user configuration by adding all system
  configuration not already listed in the user configuration items to the
  latter.}
\end{enumerate}

The \texttt{ApplySecurity(XMLNode\& ccfg)} adds security tags to the
ccfg {\XMLNode} as follows:

\begin{itemize}
\item{If the \texttt{\$X509\_USER\_PROXY} environment variable is set,
  use its value to define a \texttt{ProxyPath} tag in \texttt{ccfg}. If
  the file does not exist or can't be read exit with an error.}
\item{Otherwise, if the \texttt{\$X509\_USER\_CERT} environment
  variable is set, use its value and the value of the
  \texttt{\$X509\_USER\_KEY} environment variable to define
  \texttt{CertificatePath} and \texttt{KeyPath} tags in \texttt{ccfg}.
  If \texttt{\$X509\_USER\_KEY} is not set or either file does not
  exist or can't be read exit with an error.}
\item{Otherwise, if the merged user configuration tree (see
  \texttt{ConfTree}) contains a \texttt{ProxyPath} tag, copy it to
  \texttt{ccfg}. If the file does not exist or can't be read exit with
  an error.}
\item{Otherwise, if the merged user configuration tree contains a
  \texttt{CertificatePath} tag, copy it to \texttt{ccfg} along with the
  accompanying \texttt{KeyPath} tag. If the \texttt{KeyPath} tag is
  undefined or either file does not exist or can't be read exit with
  an error.}
\item{Otherwise, if the file \texttt{/tmp/x509up\_u + userid} exists
  add a \texttt{ProxyPath} tag in \texttt{ccfg} pointing to it.}
\item{Otherwise, add \texttt{CertificatePath} and \texttt{KeyPath}
  tags to \texttt{ccfg} pointing to
  \texttt{\$HOME/.globus/usercert.pem} and
  \texttt{\$HOME/.globus/userkey.pem}, respectively. If either file
  does not exist exit with error.}
\item{If the \texttt{\$X509\_CERT\_DIR} environment variable is set,
  use its value to define a \texttt{CACertificatesDir} tag in
  \texttt{ccfg}. If the directory does not exist, exit with an error.}
\item{Otherwise, if the user ID is not zero and the directory
  \texttt{\$HOME/.globus/certificates} exists add a
  \texttt{CACertificatesDir} tag in \texttt{ccfg} pointing to it.}
\item{Otherwise, add a \texttt{CACertificatesDir} tag in \texttt{ccfg}
  pointing to \texttt{/etc/grid-security/certificates}. If the
  directory does not exist, exit with an error.}
\end{itemize}

\subsection{{\ACCConfig}}

Locating Arc Client Components (plugins) is handled by the
{\ACCConfig} class. It inherits from \texttt{BaseConfig} and
implements only one method

\begin{shaded}
\begin{verbatim}
virtual XMLNode MakeConfig(XMLNode cfg) const;
\end{verbatim}
\end{shaded}

The \texttt{MakeConfig} method searches plugin paths for all libraries
named \texttt{libacc*}. Matching libraries are added as plugins to the
configuration object \texttt{cfg}.

\subsection{{\ClientInterface}}

The {\ClientInterface} class is a utility base class used for
configuring a client side Message Chain Component (MCC) chain and
loading it into memory. It has several specializations of increasing
complexity of the MCC chains.

\subsubsection{{\ClientTCP}}

The {\ClientTCP} class is a specialization of the {\ClientInterface}
which sets up a client MCC chain for TCP communication, and optionally
with a TLS layer on top.

\subsubsection{{\ClientHTTP}}

The {\ClientHTTP} class inherits from the {\ClientTCP} class and adds
an HTTP MCC to the chain.

\subsubsection{{\ClientSOAP}}

The {\ClientSOAP} class inherits from the {\ClientHTTP} class and adds
a SOAP MCC to the chain. Specializations of the {\TargetRetriever},
{\Submitter} and {\JobController} classes that communicate with SOAP
based services make use of this class.

\subsection{{\Sandbox}}
The {\Sandbox} class, consisting of the two methods \texttt{Add} and 
\texttt{GetCkSum}, have been created to assure a reliable resubmission 
of jobs. 
\begin{shaded}
\begin{verbatim}
static bool Add(JobDescription& jobdesc, XMLNode& info);
static std::string GetCksum(const std::string& file);
\end{verbatim}
\end{shaded}
The \texttt{Add} method  adds the job description and the checksum of 
the local input files to a {\XMLNode}. Currently this {\XMLNode} is the one 
stored in the user's local XML file upon job submission. The job 
description which is stored is the initial job description before any 
parsing has been performed. To calculate the checksum of the input 
files the \texttt{GetCkSum} method is used. The \texttt{GetCkSum} 
method returns the MD5 checksum of a given file

\section{Specialized Classes (Grid Flavour and Broker plugins)}
\label{sec:plugins}

\subsection{ARC0 Plugins}

\subsection{ARC1 Plugins}

\subsection{gLite Plugins}

\subsection{Broker plugins}
\label{sec:brokerplugins}

@@

\subsubsection{\Benchmark}

@@

\subsubsection{\FastestQueueBroker}

@@

\subsubsection{\Data}

@@

\subsubsection{\PythonBroker}

@@

\chapter{Building Command Line Interfaces}
\label{sec:cli}

Given all components listed above it is possible to write versatile
command line interfaces (cli) for grid job submission and
management. {\libarcclient} offers the following native commands:
\begin{enumerate}
\item{\texttt{arcstat} - for computing resource or grid job status 
queries.}
\item{\texttt{arcsub} - for grid job submission.}
\item{\texttt{arcget} - for downloading output of finished, cancelled 
or failed grid jobs.}
\item{\texttt{arckill} - for terminating grid jobs.}
\item{\texttt{arcclean} - for removing a grid job's session directory 
including all contents.}
\item{\texttt{arccat} - for performing the \texttt{cat} command to a 
running grid job's std out or std error file.}
\item{\texttt{arcsync} - for synchronising the information in the user's 
local XML file\footnote{By default \$HOME/.arc/jobs.xml} about active jobs.}
\item{\texttt{arcresub} - for starting an entire job over on either the 
same or a new computing resource.}
\item{\texttt{arcmigrate} - for moving a queuing job from one A-REX 
server to another.}
\end{enumerate}

Each of the commands above are encoded within one C++ file with the
following structure, here exemplified with the arcget command:

\begin{shaded}
\begin{verbatim}
#ifdef HAVE_CONFIG_H
#include <config.h>
#endif

#include <iostream>
#include <list>
#include <string>

#include <arc/ArcLocation.h>
#include <arc/IString.h>
#include <arc/Logger.h>
#include <arc/OptionParser.h>
#include <arc/client/JobController.h>
#include <arc/client/JobSupervisor.h>
#include <arc/client/UserConfig.h>

int main(int argc, char **argv) {

  setlocale(LC_ALL, "");

  Arc::Logger logger(Arc::Logger::getRootLogger(), "arcget");
  Arc::LogStream logcerr(std::cerr);
  Arc::Logger::getRootLogger().addDestination(logcerr);
  Arc::Logger::getRootLogger().setThreshold(Arc::WARNING);

  Arc::ArcLocation::Init(argv[0]);

  Arc::OptionParser options(istring("[job ...]"),
                            istring("The arcget command is used for "
                                    "retrieving the results from a job."),
                            istring("Argument to -c has the format "
                                    "Flavour:URL e.g.\n"
                                    "ARC0:ldap://grid.tsl.uu.se:2135/"
                                    "nordugrid-cluster-name=grid.tsl.uu.se,"
                                    "Mds-Vo-name=local,o=grid"));

  bool all = false;
  options.AddOption('a', "all",
                    istring("all jobs"),
                    all);

  // Removed most of the option definition from this write-up to
  // save space. See the real source file for the complete list.
  // ...

  bool version = false;
  options.AddOption('v', "version", istring("print version information"),
                    version);

  std::list<std::string> jobs = options.Parse(argc, argv);

  if (!debug.empty())
    Arc::Logger::getRootLogger().setThreshold(Arc::string_to_level(debug));

  Arc::UserConfig usercfg(conffile);
  if (!usercfg) {
    logger.msg(Arc::ERROR, "Failed configuration initialization");
    return 1;
  }

  if (debug.empty() && usercfg.ConfTree()["Debug"]) {
    debug = (std::string)usercfg.ConfTree()["Debug"];
    Arc::Logger::getRootLogger().setThreshold(Arc::string_to_level(debug));
  }

  if (version) {
    std::cout << Arc::IString("%s version %s", "arcget", VERSION)
              << std::endl;
    return 0;
  }

  if (jobs.empty() && joblist.empty() && !all) {
    logger.msg(Arc::ERROR, "No jobs given");
    return 1;
  }

  if (joblist.empty())
    joblist = usercfg.JobListFile();

  Arc::JobSupervisor jobmaster(usercfg, jobs, clusters, joblist);

  std::list<Arc::JobController*> jobcont = jobmaster.GetJobControllers();

  if (jobcont.empty()) {
    logger.msg(Arc::ERROR, "No job controllers loaded");
    return 1;
  }

  int retval = 0;
  for (std::list<Arc::JobController*>::iterator it = jobcont.begin();
       it != jobcont.end(); it++)
    if (!(*it)->Get(status, downloaddir, keep, timeout))
      retval = 1;

  return retval;
}
\end{verbatim}
\end{shaded}

@@

\chapter{Job Inner Representation}
\label{app:jobinnerrepresentation}

http://svn.nordugrid.org/trac/nordugrid/browser/arc1/trunk/doc/client/JobInnerRepresentation.ods

>>>>

\chapter{The ARC Brokering Module}
\label{sec:brokering}

@@

\section{Broker plugins}
\label{sec:brokerplugins}

@@

\subsection{\Benchmark}

@@

\subsection{\FastestQueueBroker}

@@

\subsection{\Data}

@@

\subsection{\PythonBroker}

@@

\chapter{Job Description}
\label{sec:jobdesc}

\chapter{Grid Flavour Plugins)}
\label{sec:plugins}

\section{ARC0 Plugins}

\section{ARC1 Plugins}

\section{gLite Plugins}

@@

\chapter{Job Status mapping}
\label{app:broker-mapping}
